### 2024-10-20 analysis/analysis.qmd
figure 3

```{r}
O <- find.outliers(m.cor)
# 6 datasets identified as outliers, without them the r drops to 0.5781
infan <- InfluenceAnalysis(m.cor)
print(eggers.test(m.cor))
```

>>>>

```{r}
#| eval: false
#| echo: false
O <- find.outliers(m.cor) # 13 remaining out of 24
# 6 datasets identified as outliers, without them the r drops to 0.5781
infan <- InfluenceAnalysis(m.cor)
print(eggers.test(m.cor))

# 10% most precise studies (Stanley, Jarrel, Doucouliagos 2010)
thres<-quantile(m.cor$seTE,0.1)
ind<-m.cor$seTE<=as.numeric(thres)

m.cor10pct <- update(m.cor, subset = which(ind))

### 2024-10-20 manuscript/_figure3.qmd
figure 3

```{r}
#| label: fig2
#| fig-width: 16
#| fig-height: 6
#| echo: false
#| fig.cap: > 
#|   Forest and funnel plots of valence predictions from the MER models.

>>>>

```{r}
#| label: fig3
#| fig-width: 16
#| fig-height: 6
#| echo: false
#| fig.cap: > 
#|   Forest (A) and funnel (B) plots of the best arousal models from all MER studies.

### 2024-10-20 manuscript/manuscript.qmd
figure 3

Further analysis of between-study heterogeneity, as indexed by the $\tau^2$ (0.138) and Higgins & Thompson's $I^2$ statistic [@higgins2002quantifying] at 98.2%, reveals substantial heterogeneity. Since $I^2$ is heavily influenced by study size (with larger N leading to lower sampling error), its value may be less insightful in this context. In contrast, $\tau^2$, which is less sentive to the number of studies and directly linked to the outcome metric (_r_), provides a more reliable measure of heterogeneity in this case.

To better understand the effects across studies and the nature of the observed heterogeneity, Figure 2 presents a forest plot of the random-effects model, based on the best-performing models from all studies. The range of prediction values (correlations) is broad, spanning from 0.13 to 0.92, with all studies except Koh et al. (2023) demonstrating evidence of positive correlations. A mean estimate of 0.66 is achieved by 15 out of the 24 models. While the confidence intervals are generally narrow due to the large sample sizes in each study, there are exceptions, such as smaller sample sizes in @beveridge2018po (n = 20), @saizclar2022pr (n = 40), and in @griffiths2021am (n = 40).

@@

When analyzing the data by modeling techniques, we identified five sub-groups. Notably, linear models (LM) and flexible discriminants (FD) were the most common, with 8 and 6 studies, respectively, allowing for more confident interpretations. Linear models achieved the highest prediction rate (_r_ = 0.784, 95% CI: 0.625–0.881), though this may be influenced by the smaller datasets typically used in these studies. These studies also exhibited substantially higher heterogeneity ($\tau^2$ = 0.137) compared to other techniques, where $\tau^2$ values were less than half of this. Flexible discriminants performed at a similar level to the overall model average (_r_ = 0.656, 95% CI: 0.484–0.779). The relatively poor performance of neural network (NN) models (_r_ = 0.340, 95% CI: -0.097–0.668) is difficult to explain without a deeper examination of the specific model architectures and the stimuli used in these studies.

We also ran the sub-grouping analyses across a combination of stimulus genres (single vs mixed) and number of the features to explore where the differences in model success might lie. For this purpose, we grouped the studies into small single genre/multigenre studies (1), medium single genre/multigenre studies (2), and medium-large single genre/multigenre studies (3), and huge multigenre studies (4). The small single genre/multigenre studies generally performed best (_r_ = 0.836, 95% CI: -0.197-0.989), followed by huge multi-genre studies (_r_ = 0.720, 95% CI: -0.189-0.965) while the medium and medium-large sized studies performance was between close the overall average (medium-large, _r_ = 0.669, 95% CI: 0.347-0.850 and medium _r_ = 0.587, 95% CI: 0.433-0.708). The heterogeneity was lowest in the huge multigenre studies ($\tau^2$ = 0.013) and highest in the small single genre/multigenre studies ($\tau^2$ = 0.318).

@@

Moving on the arousal, we carry out the same meta-analytical analysis applying the random-effects model to arousal. Table 3 and Figure 2 shows the same outputs as was done for valence describing the broad pattern of results in tabular and in forest plot formats. Table 3 give

>>>>

Further analysis of between-study heterogeneity, as indexed by the $\tau^2$ (0.138) and Higgins & Thompson's $I^2$ statistic [@higgins2002quantifying] at 98.2%, reveals substantial heterogeneity. Since $I^2$ is heavily influenced by study size (with larger N leading to lower sampling error), its value may be less insightful in this context. In contrast, $\tau^2$, which is less sensitive to the number of studies and directly linked to the outcome metric (_r_), provides a more reliable measure of heterogeneity in this case. Also, we note that because the overall heterogeneity in the data is high, we are cautious in our interpretation of the publication bias [@van-aertwicherts_2016].

To better understand the effects across studies and the nature of the observed heterogeneity, Figure 2 presents (A) a forest and (B) funnel plot of the random-effects model, based on the best-performing models from all studies. In terms of the forest plot, the range of prediction values (correlations) is broad, spanning from 0.13 to 0.92, with all studies except Koh et al. (2023) demonstrating evidence of positive correlations. A mean estimate of 0.66 is achieved by 15 out of the 24 models. While the confidence intervals are generally narrow due to the large sample sizes in each study, there are exceptions, such as smaller sample sizes in @beveridge2018po (n = 20), @saizclar2022pr (n = 40), and in @griffiths2021am (n = 40). The funnel plot in panel B of Figure 2 shows clustering at the top of the plot (studies with low standard error) and no assumed larger diversity in the correlations when the error rates increase. However, there is no clear asymmetry in the plot, verified by non-significant Egger's test ($\beta$=5.00, CI95% -0.78-10.78, _t_ = 1.70, _p_ = 0.104, @eggersmith_1997). Coming back to the mean of valence correlation of 0.66 by all studies and the possible impact of study heterogeneity on this estimation, we also calculated the correlation without the studies that lie outside the 95% CI for pooled effect. This left 13 studies in the data and resulted in the meta-analytical pooled correlation of 0.649 (CI95% 0.598-0.695). In other words, despite the large variation in the correlations and standard errors across the studies, this variation in itself does not seem to be a significant driver behind the overall effect.

@@

When analyzing the studies across the five modeling techniques used. Notably, linear models (LM) and flexible discriminants (FD) were the most common, with 8 and 6 studies, respectively, allowing for more confident interpretations. Linear models achieved the highest prediction rate (_r_ = 0.784, 95% CI: 0.625–0.881), though this may be influenced by the smaller datasets typically used in these studies. These studies also exhibited substantially higher heterogeneity ($\tau^2$ = 0.137) compared to other techniques, where $\tau^2$ values were less than half of this. Flexible discriminants performed at a similar level to the overall model average (_r_ = 0.656, 95% CI: 0.484–0.779). The relatively poor performance of the neural network (NN) models (_r_ = 0.340, 95% CI: -0.097–0.668) is difficult to explain without a deeper examination of the specific model architectures and the stimuli used in these studies.

We also ran the sub-grouping analyses across a combination of stimulus genres (single vs mixed) and number of the features to explore where the differences in the model prediction rates might lie. For this purpose, we grouped the studies into small single genre/multigenre studies, medium single genre/multigenre studies, and medium-large single genre/multigenre studies, and huge multigenre studies. The small single genre/multigenre studies generally performed best (_r_ = 0.836, 95% CI: -0.197-0.989), followed by huge multi-genre studies (_r_ = 0.720, 95% CI: -0.189-0.965) while the medium and medium-large sized studies performance was between close the overall average (medium-large, _r_ = 0.669, 95% CI: 0.347-0.850 and medium _r_ = 0.587, 95% CI: 0.433-0.708). The heterogeneity was lowest in the huge multigenre studies ($\tau^2$ = 0.013) and highest in the small single genre/multigenre studies ($\tau^2$ = 0.318).

@@

Moving on the arousal, we carry out the same meta-analytical analysis applying the random-effects model to arousal. Table 3 and Figure 3 show the same outputs as was done for valence describing the broad pattern of results in tabular format, and visually illustrate the spread and heterogeneity of all studies.

Table 3 indicates that the overall correlation across the studies using the best performing model out of each study (Max) is 0.807 (CI95% 0.745-0.855). If we examine all the models, the correlation drops to 0.796, only marginally lower.

The indicators of heterogeneity ($\tau^2$ = 0.155 and $I^2$=96.8%) suggest high
